Estimating Information Transfer in Hard Parameter Sharing via Precise Bias-variance Asymptotics

### 2021-07-15 revision_journal/setup.tex
sec 4 wip

\section{Preliminaries}\label{sec_HPS}
We begin by formally defining the data model involving large dimensional random matrices together with the underling assumptions.
We define the model shift and covariate shift settings, in which we will analyze transfer learning in the next section.
Then, we describe the estimators for the model using two-layer linear neural networks.
Finally, we present a bias-variance decomposition of our estimators.
We explain why this decomposition is crucial for analyzing information transfer and the need for new techniques in the analysis.
Our setup in this section concerns the case of a single data source.
Later on in Section \ref{sec_same}, we will extend the setup to the case of multiple data sources.
%In Section \ref{sec_same}, we will consider a simple extension to a multi-task learning setting with more than two tasks and  the same covariates for all tasks. We will give the asymptotic limit of the predication loss for the HPS estimator, which provides useful insights into the more rich multi-task learning theory. %Due to length constraint, we will explore the multi-task learning setting in greater details in other works.

@@

%We describe our estimators that combine the information from both datasets.
We learn a two-layer linear neural network with parameters $A \in \real^{p\times r}$, $B_1 \in \real^{r}$, and $B_2 \in \real^r$ by minimizing the following optimization objective:
\begin{align}\label{eq_hps}
    f(A, B_1, B_2) = \bignorm{X^{(1)} A B_1 - Y^{(1)}}_2^2 + \bignorm{X^{(2)} A B_2 - Y^{(2)}}_2^2.
\end{align}
The above two-layer neural network (also called hard parameter sharing \cite{C97}) captures the intuition that both datasets share the feature space (i.e. the subspace spanned by the columns of $A$) while each having a separate prediction head.
Suppose that $(\hat{A}, \hat{B_1}, \hat{B_2})$ is a minimizer of $f(\cdot)$.
We define the hard parameter sharing estimator for task $i$ as
\[ \hat{\beta}_i^{\MTL} \define \hat{B} \hat{A}_i. \]
Our study of such estimators is motivated by the fact that hard paratemer sharing is widely used in empirical studies of multi-task learning \cite{R17}.
\todo{Later on in Section \ref{sec_diff}, we will further compare the HPS estimator to other natural transfer learning estimators.}

We measure the performance of $\hat{\beta}_i^{\MTL}$ through the out-of-sample predication risk (or test loss).
Consider a datapoint $(x,y)$ generated from the same model as dataset $i$: $y= x^\top \beta^{(i)} + \ve$.
The expected predication risk (under mean squared error) is given by
$$\exarg{x, \varepsilon}{\left\|y-x^\top \hat{\beta}_i^{\MTL} \right\|^2}= \left\|\big(\Sigma^{(i)}\big)^{1/2} \left(\hat{\beta}_i^{\MTL} - \beta^{(i)}\right)\right\|^2 + \sigma^2.$$
The excess risk is defined without the constant term $\sigma^2$:
\be\label{HPS_loss}
    L(\hat{\beta}_i^{\MTL}):= \left\| \big(\Sigma^{(i)}\big)^{1/2} \left(\hat{\beta}_i^{\MTL} - \beta^{(i)}\right)\right\|^2 .
\ee

@@

\begin{proof}
    Since both $n_1$ and $n_2$ are at least $(1 + \tau) p$, the inverse of both ${X^{(1)}}^{\top} X^{(1)}$ and ${X^{(2)}}^{\top} X^{(2)}$ exists.
    Thus, both $\hat{\beta}_1^{\STL}$ and $\hat{\beta}_2^{\STL}$ are well-defined.
    The global minimum of each summand of equation \eqref{eq_hps} is achieved if and only if $\hat{\beta}_1^{\STL}$ and $\hat{\beta}_2^{\STL}$ are both in the column subspace of $A$.
    In this case, $\hat{\beta}_1^{\MTL} = A B_1$ must be equal to $\hat{\beta}_1^{\STL}$ (same for $\hat{\beta}_2^{\MTL}$).
\end{proof}
%Our goal is to characterize the 
%$The minimizers of $f(\cdot)$
%\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}

@@

\todo{edit the transition here} We show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.
The proof of Proposition \ref{lem_hat_v} can be found in Section \ref{app_iso_cov_prop}.

\begin{proposition}[Optimum under the random-effect model]\label{lem_hat_v}
%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
    Suppose Assumption \ref{assm_big1} and the above random-effect model under equation \eqref{eq_re} holds. %in Example \ref{ex_same_cov} hold.
    Suppose that for a constant $c_0>0$,
	\be\label{para_rel}
	    \|\beta_0\|^2 \ge p^{c_0}\mu^2 +p^{-1/2+c_0}\sigma^2.
	\ee
    Then we have that for any small constant $c>0$ and large constant $ C>0$,
	%Let $c$ be a sufficiently small fixed constant.
	%In the setting of Corollary \ref{cor_MTL_loss},
%There exists a constant $C>0$ such that
	\be\label{hatw_add1}
	 \hat a =1+ \OO\left(\frac{\mu^2}{\|\beta_0\|^2} + p^{-\frac 1 4 + c} \frac{\mu+\sigma}{\|\beta_0\|} + p^{-C}\right) \quad \text{w.h.p.}
	\ee
\end{proposition}
In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
\todo{change $d$ to $\mu$ because a reviewer complained}
%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
%%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
%More precisely, %we have
%$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
%where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
%and $\wt \beta^{(i)}$ denotes the $i$-th
%%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
%task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
%We emphasize that unlike Theorem \ref{cor_MTL_loss}, for Proposition \ref{lem_hat_v} we do not assume $\Sigma^{(1)}=\Sigma^{(2)}$ and the Gaussian distributions of the entries of $Z^{(1)}$ and $Z^{(2)}$.
%In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far. %\FY{What is known so far about this topic?}

%{\cor discuss about the bias-variance trade-off}
%However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.

@@

Next, we provide the bias-variance decomposition of the excess risk under this setting.
Without loss of generality, we focus on task two's excess risk $L(\hat{\beta}^{\MTL}_2)$.
As a remark, for general $r$, problem \eqref{eq_hps} is non-convex since $f(\cdot)$ is a degree-four polynomial.
Nevertheless, the setting when $r = 1$ remains tractable since we can write a closed-form solution of $A$ given any (scalar) $B_1$ and $B_2$.
Since $B_1$ and $B_2$ are both scalars, let $a = B_1 / B_2$.
Let $\hat{\Sigma}(a) \define a^2 (X^{(1)})^{\top} X^{(1)} + (X^{(2)})^{\top} X^{(2)}$ be a weighted combination of the sample covariance matrices.
We present a bias-variance decomposition of $L(\hat{\beta}^{\MTL}_2)$ for the setting of $r = 1$ as follows.

\begin{proposition}[Bias-variance decomposition]\label{lem_HPS_loss}
     Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$ and $\lambda\in [0,1]$:
    \begin{align}
        L(\hat{\beta}_2^{\MTL}) =& \left( 1+ \OO(p^{-1/2+c})\right)\cdot \left(L_{\bias} (a) + L_{\var}(a)\right) %\nonumber\\
        + \OO \left( p^{-C}\big( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\big)   \right), \label{L_HPS_simple}
    \end{align}
    where the bias and variance equations are defined as follows:
    \begin{align}
        L_{\bias} (a) &\define \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2,  \label{Lbias} \\
        L_{\var}(a)   &\define \sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }}.  \label{Lvar}
    \end{align}
\end{proposition}

Equation \eqref{L_HPS_simple} shows that the excess risk of the HPS estimator admits a clean bias-variance decomposition plus lower-order terms that decrease to zero with the dimension $p$.
Since equation \eqref{L_HPS_simple} holds uniformly for all $a\in \R$, we can apply the result to $a = \hat{B}_1 / \hat{B}_2$, for any $\hat{B}_1$ and $\hat{B}_2$ that may depend on $\ve^{(1)}$ and $\ve^{(2)}$ (after solving problem \eqref{eq_hps}).
%The proof of Proposition \ref{lem_HPS_loss} involves
We briefly describe why Proposition \ref{lem_HPS_loss} holds.
First, suppose that $a$ is an arbitrary value that is independent of the random noise vectors$ \varepsilon^{(1)}$ and $\varepsilon^{(2)}$.
By taking the expectation over both of them, we get the following result:
\be\label{partial-L}
    \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}) } = L_{\bias} (a) + L_{\var}(a).
\ee
Secondly, using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma.
For a fixed $a\in \R$, the proof of \eqref{L_HPS_simple} is based on the sharp concentration bounds in Lemma \ref{largedeviation} of Section \ref{??}.
To extend uniformly to all $a\in \R$, we will use a standard $\ve$-net argument, which leads to a small error $ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right) $. Note that this error is negligible unless $\beta^{(1)}$ and $ a\beta^{(2)}$ cancel each other almost exactly, and the noise variance $\sigma$ is very small.
The proof of Proposition \ref{lem_HPS_loss} can be found in Section  \ref{app_firstpf}.
%Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{, li2020transfer}:
%$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$

@@

\paragraph{Connection to information transfer.} To be precise, we say that task one provides a positive transfer to task two, if the excess risk $L(\hat{\beta}_2^{\MTL})$ is smaller than $L(\hat{\beta}_2^{\STL})$.
Otherwise, we say that task one provides a negative transfer to task two.
We now illustrate that the bias-variance decomposition of Proposition \ref{lem_HPS_loss} characterizes whether or not the information transfer is positive.

@@

\begin{lemma}[Variance asymtotics of OLS estimators, cf. Theorem 2.4 of \citet{isotropic} and Theorem 3.14 of \citet{DY}]\label{fact_tr}
	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
	Under Assumption \ref{assm_big1}, we have that for any deterministic  matrix $\Sigma\in\real^{p\times p}$,
		\[ \bigtr{\Sigma \Big((X^{(2)})^\top X^{(2)} \Big)^{-1}  } %= \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  }
		= \frac{1}{n_2 - p}\bigtr{\Sigma (\Sigma^{(2)})^{-1}} +  \OO\left( \frac{p^{\e}}{\sqrt{n_2 p}}\cdot \frac{p}{n_2}\|\Sigma\|_{op} \right) \]
		with high probability for any small constant $\e>0$.
\end{lemma}
\todo{the scaling $\sqrt{n_2}$ above doesn't seem correct}

@@

On the other hand, characterizing the risk of the HPS estimator requires dealing with several challenges.
First, characterizing bias (cf. equation \eqref{Lbias}) introduces the issue of \textit{model shift}, when $\beta^{(1)}$ differs from $\beta^{(2)}$.
Second, characterizing variance (cf. equation \eqref{Lvar}) introduces  the issue of \textit{covariate shift}, when $\Sigma^{(1)}$ differs from $\Sigma^{(2)}$.
Our main results in the next section provide precise bias-variance asymptotics under either (or both) shift(s).

>>>>

\section{Preliminaries}\label{sec_HPS}
We begin by formally defining the data model involving large dimensional random matrices together with the underling assumptions.
We define the covariate shift and model shift settings.
Then, we describe the HPS estimators for these settings using two-layer linear neural networks.
Finally, we present a bias-variance decomposition of the HPS estimators.
We explain why this decomposition is crucial for analyzing information transfer and the need for new techniques in the analysis.
Our setup in this section concerns the case of a single data source.
Later on in Section \ref{sec_same}, we will extend the setup to the case of multiple data sources.
%In Section \ref{sec_same}, we will consider a simple extension to a multi-task learning setting with more than two tasks and  the same covariates for all tasks. We will give the asymptotic limit of the predication loss for the HPS estimator, which provides useful insights into the more rich multi-task learning theory. %Due to length constraint, we will explore the multi-task learning setting in greater details in other works.

@@

%We describe our estimators that combine the information from both datasets.
We learn a two-layer linear neural network with parameters $A \in \real^{p\times r}$, $B_1 \in \real^{r}$, and $B_2 \in \real^r$ by minimizing the following optimization objective:
\begin{align}\label{eq_hps}
    f(A, B_1, B_2) = \bignorm{X^{(1)} A B_1 - Y^{(1)}}_2^2 + \bignorm{X^{(2)} A B_2 - Y^{(2)}}_2^2.
\end{align}
The above two-layer neural network (also called hard parameter sharing \cite{C97}) captures the intuition that both datasets share the feature space (i.e. the subspace spanned by the columns of $A$) while each having a separate prediction head.
Suppose that $(\hat{A}, \hat{B_1}, \hat{B_2})$ is a minimizer of $f(\cdot)$.
We define the hard parameter sharing estimator for task $i$ as
\[ \hat{\beta}_i^{\MTL} \define \hat{B} \hat{A}_i. \]
Our study of such estimators is motivated by the fact that hard parameter sharing is widely used in empirical studies of multi-task learning \cite{R17}.
Later on in Section \ref{sec_diff}, we will evaluate the performance of HPS estimators against several natural transfer learning estimators.

We measure the performance of $\hat{\beta}_i^{\MTL}$ over samples $(x,y)$ generated from the $i$-th data model: $y= x^\top \beta^{(i)} + \ve$.
The expected prediction risk (under mean squared loss) is given by
$$\exarg{x, \varepsilon}{\left\|y-x^\top \hat{\beta}_i^{\MTL} \right\|^2}= \left\|\big(\Sigma^{(i)}\big)^{1/2} \left(\hat{\beta}_i^{\MTL} - \beta^{(i)}\right)\right\|^2 + \sigma^2.$$
The excess risk is the difference between the above risk and the expected risk of the population risk optimizer (which is equal to $\sigma^2$):
\be\label{HPS_loss}
    L(\hat{\beta}_i^{\MTL}):= \left\| \big(\Sigma^{(i)}\big)^{1/2} \left(\hat{\beta}_i^{\MTL} - \beta^{(i)}\right)\right\|^2 .
\ee

@@

\begin{proof}
    Since both $n_1$ and $n_2$ are at least $(1 + \tau) p$, the inverse of both ${X^{(1)}}^{\top} X^{(1)}$ and ${X^{(2)}}^{\top} X^{(2)}$ exists.
    Thus, both $\hat{\beta}_1^{\STL}$ and $\hat{\beta}_2^{\STL}$ are well-defined.
    The global minimum of each summand of equation \eqref{eq_hps} is achieved if and only if $\hat{\beta}_1^{\STL}$ and $\hat{\beta}_2^{\STL}$ are both in the column subspace of $A$.
    In this case, $\hat{\beta}_1^{\MTL} = A B_1$ must be equal to $\hat{\beta}_1^{\STL}$ (same for $\hat{\beta}_2^{\MTL}$).
\end{proof}

@@

@@

Next, we provide the bias-variance decomposition of the excess risk under this setting.
Without loss of generality, we focus on task two's excess risk $L(\hat{\beta}^{\MTL}_2)$.
As a remark, for general $r$, problem \eqref{eq_hps} is non-convex since $f(\cdot)$ is a degree-four polynomial.
Nevertheless, the setting when $r = 1$ remains tractable since we can write a closed-form solution of $A$ given any (scalar) $B_1$ and $B_2$.
Since $B_1$ and $B_2$ are both scalars, let $a = B_1 / B_2$.
Let $\hat{\Sigma}(a) \define a^2 (X^{(1)})^{\top} X^{(1)} + (X^{(2)})^{\top} X^{(2)}$ be a weighted combination of the sample covariance matrices.
We present a bias-variance decomposition of $L(\hat{\beta}^{\MTL}_2)$ for the setting of $r = 1$ as follows.
We say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.

\begin{proposition}[Bias-variance decomposition]\label{lem_HPS_loss}
     Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists an event $\Xi$, on which the following estimates hold uniformly in $a\in \R$ and $\lambda\in [0,1]$ w.h.p.:
    \begin{align}
        L(\hat{\beta}_2^{\MTL}) =& \left( 1+ \OO(p^{-1/2+c})\right)\cdot \left(L_{\bias} (a) + L_{\var}(a)\right) %\nonumber\\
        + \OO \left( p^{-C}\big( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\big)   \right), \label{L_HPS_simple}
    \end{align}
    where the bias and variance equations are defined as follows:
    \begin{align}
        L_{\bias} (a) &\define \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2,  \label{Lbias} \\
        L_{\var}(a)   &\define \sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }}.  \label{Lvar}
    \end{align}
\end{proposition}

Equation \eqref{L_HPS_simple} shows that the excess risk of the HPS estimator admits a clean bias-variance decomposition plus lower-order terms that decrease to zero with the dimension $p$.
Since equation \eqref{L_HPS_simple} holds uniformly for all $a\in \R$, we can apply the result to $\hat a = \hat{B}_1 / \hat{B}_2$, for any $\hat{B}_1$ and $\hat{B}_2$ that may depend on $\ve^{(1)}$ and $\ve^{(2)}$ (after solving problem \eqref{eq_hps}).
%The proof of Proposition \ref{lem_HPS_loss} involves
We briefly describe why Proposition \ref{lem_HPS_loss} holds.
First, suppose that $a$ is an arbitrary value that is independent of the random noise vectors $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$.
By taking the expectation over both of them, we get the following result:
\be\label{partial-L}
    \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}) } = L_{\bias} (\hat a) + L_{\var}(\hat a).
\ee
Secondly, using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma.
For a fixed $a\in \R$, the proof of \eqref{L_HPS_simple} is based on the sharp concentration bounds in Lemma \ref{largedeviation} of Section \ref{??}.
To extend uniformly to all $a\in \R$, we will use a standard $\ve$-net argument, which leads to a small error $ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right) $. Note that this error is negligible unless $\beta^{(1)}$ and $ a\beta^{(2)}$ cancel each other almost exactly, and the noise variance $\sigma$ is very small.
The proof of Proposition \ref{lem_HPS_loss} can be found in Section  \ref{app_firstpf}.

Equation \eqref{partial-L} suggests that the bias and variance of HPS both depend on the scalar $\hat a$.
We provide some intuition about this scalar in the setting of random-effect models.
We show that under natural assumptions, the global minimizer $\hat a = \hat B_1 / \hat B_2$ is approximately equal to $1$.
The proof of Proposition \ref{lem_hat_v} can be found in Section \ref{app_iso_cov_prop}.

\begin{proposition}[Random-effect model]\label{lem_hat_v}
    Suppose Assumption \ref{assm_big1} and the random-effect model under equation \eqref{eq_re} holds. 
    Suppose that for a constant $c_0>0$,
	\be\label{para_rel}
	    \|\beta_0\|^2 \ge p^{c_0}\mu^2 +p^{-1/2+c_0}\sigma^2.
	\ee
    Then we have that for any small constant $c>0$ and large constant $ C>0$,
	%Let $c$ be a sufficiently small fixed constant.
	%In the setting of Corollary \ref{cor_MTL_loss},
%There exists a constant $C>0$ such that
	\be\label{hatw_add1}
	 \hat a =1+ \OO\left(\frac{\mu^2}{\|\beta_0\|^2} + p^{-\frac 1 4 + c} \frac{\mu+\sigma}{\|\beta_0\|} + p^{-C}\right) \quad \text{w.h.p.}
	\ee
\end{proposition}
\todo{change $d$ to $\mu$ because a reviewer complained}
%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
%%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
%More precisely, %we have
%$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
%where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
%and $\wt \beta^{(i)}$ denotes the $i$-th
%%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
%task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
%We emphasize that unlike Theorem \ref{cor_MTL_loss}, for Proposition \ref{lem_hat_v} we do not assume $\Sigma^{(1)}=\Sigma^{(2)}$ and the Gaussian distributions of the entries of $Z^{(1)}$ and $Z^{(2)}$.
%In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far. %\FY{What is known so far about this topic?}

%{\cor discuss about the bias-variance trade-off}
%However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
%Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{, li2020transfer}:
%$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$

@@

\paragraph{Connection to information transfer.} To be precise, we say that task one provides a \textit{positive transfer} to task two, if the excess risk $L(\hat{\beta}_2^{\MTL})$ is smaller than $L(\hat{\beta}_2^{\STL})$.
Otherwise, we say that task one provides a \textit{negative transfer} to task two.
We now illustrate that the bias-variance decomposition of Proposition \ref{lem_HPS_loss} characterizes whether or not the information transfer is positive.

@@

\begin{lemma}[Variance estimates of OLS estimators, cf. Theorem 2.4 of \citet{isotropic} and Theorem 3.14 of \citet{DY}]\label{fact_tr}
	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
	Under Assumption \ref{assm_big1}, we have that for any deterministic  matrix $\Sigma\in\real^{p\times p}$,
		\[ \bigtr{\Sigma \Big((X^{(2)})^\top X^{(2)} \Big)^{-1}  } %= \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  }
		= \frac{1}{n_2 - p}\bigtr{\Sigma (\Sigma^{(2)})^{-1}} +  \OO\left( \frac{p^{\e}}{\sqrt{n_2 p}}\cdot \frac{p}{n_2}\|\Sigma\|_{op} \right) \]
		with high probability for any small constant $\e>0$.
\end{lemma}
\todo{the scaling $\sqrt{n_2}$ above doesn't seem correct}

@@

On the other hand, characterizing the risk of the HPS estimator requires dealing with several challenges.
First, characterizing bias (cf. equation \eqref{Lbias}) introduces the issue of \textit{model shift}, when $\beta^{(1)}$ differs from $\beta^{(2)}$.
Second, characterizing variance (cf. equation \eqref{Lvar}) introduces  the issue of \textit{covariate shift}, when $\Sigma^{(1)}$ differs from $\Sigma^{(2)}$.
Our main results in the next section provide precise bias-variance asymptotics under (either or both) covariate and model shifts.
